A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-15 tex/codatadp.tex
more

\begin{table}[tbh!]
\begin{center}\begin{tabular}{l@{\kern1.5em}c@{\kern.5em}c@{\kern.5em}c@{\kern1.5em}c}
  & \HD{Distro} & \HD{AFP} & \HD{\gandl} & All
\\[1pt] %%% TYPESETTING HACK
\midrule
%$\enatT$
\\[-9pt] %%% TYPESETTING HACK
No decision procedure
  & 800 & 922 & 450 & 2172 \\
Codatatypes without bisimilarity
  & 810 & 936 & 470 & 2216 \\
Codatatypes with bisimilarity
  & 811 & 939 & 472 & 2222 \\
Datatypes without cyclicity
  & 815 & 947 & 469 & 2231 \\
Datatypes with cyclicity
  & 818 & 953 & 470 & 2241 \\
Full decision procedure
  & 840 & 970 & 490 & 2300 \\[\jot]
Total number of goals
  & 1211\phantom{0} & 1121\phantom{0} & 899 & 3001
\end{tabular}\end{center}
\caption{Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table}

>>>>

\begin{table}[tbh!]
\begin{center}\begin{tabular}{l@{\kern1.5em}c@{\kern.5em}c@{\kern.5em}c@{\kern1.5em}c}
  & \HD{Distro} & \HD{AFP} & \HD{\gandl} & All
\\[1pt] %%% TYPESETTING HACK
\midrule
%$\enatT$
\\[-9pt] %%% TYPESETTING HACK
No decision procedure
  & 401 & 922 & \phantom{0}39 & 1122 \\
Codatatypes without bisimilarity
  & 410 & 936 & \phantom{0}45 & 1136 \\
Codatatypes with bisimilarity
  & 411 & 939 & \phantom{0}48 & 1139 \\
Datatypes without cyclicity
  & 415 & 947 & \phantom{0}43 & 1147 \\
Datatypes with cyclicity
  & 418 & 953 & \phantom{0}44 & 1153 \\
Full decision procedure
  & 440 & 970 & \phantom{0}49 & 1170 \\[\jot]
Total number of goals
  & 879 & 2974\phantom{0} & 117 & 3970
\end{tabular}\end{center}
\caption{Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table}
